\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[french]{babel}
\usepackage{amsmath, amsfonts, amssymb}
\usepackage{verbatim}
\usepackage{amsthm}
\usepackage{geometry}
\usepackage{array}
\usepackage{caption}
\usepackage{graphicx}
\usepackage{float} 
\usepackage{hyperref}
\usepackage{adjustbox}
\usepackage{nomencl}
\usepackage{algorithm}
\usepackage{algorithmic}


% taille des marges
\geometry{hmargin=2cm,vmargin=2.5cm}

\title{Absorbing Boundary Layers in Time Domain Elastodynamics: Two-Dimensional Perfectly Matched Layer}
\author{Poulain Alexandre}
\date{\today}
\def\doubleunderline#1{\underline{\underline{#1}}}


\begin{document}
\pagestyle{empty}
\input{tex/titlepage}

\newpage
\renewcommand{\abstractname}{Abstract}
\begin{abstract}
%% Background (short)
% What is known
Absorbing boundary layers is a common method to solve numerically wave propagation phenomena in infinite or unbounded domains. Several techniques exist to construct these boundaries such as the introduction of Rayleigh damping in the absorbing layer or as presented in this report, perfectly matched layers (PML). They find their application in many fields such as electromagnetism and elastodynamics.   
% What is not known
Due to the complexity of the formulation of these PMLs, their construction and use remain a challenge. A large number of formulations and implementations have been proposed through the years to tackle some problems such as instability and performance.  
%% Methods (long)
% What was done
We attend in this report to present the formulation of a stable unsplit field two-dimensional perfectly matched layer based on the weak form of the equations of elastodynamics. 

\noindent First of all, the presentation of the construction of the PML will be detailed, including an extensive description of the governing equations. During this description, we will also see how the PML is able to attenuate waves. This will be followed by the implementation of the scheme in Akantu: an open-source finite-element software developed in the Computational Solid Mechanics Laboratory of the EPFL. The algorithm with the main steps of the scheme will be presented.
The numerical stability of the two dimensional unsplit field PML has never been demonstrated in the context of elastodynamics. 
Thus the method employed to prove the stability will be described and the results will be analyzed. The implicit and explicit schemes associated with the PML will be proved to be respectively unconditionally and conditionally stable.  Some of the key features of the PML will also be highlighted by this analysis, such as the postponing of the critical time step, for which the explicit scheme becomes unstable.
The results on two test cases will be reviewed in the last part of this report and a special attention will be dedicated to the reflection of the waves since this parameter represents the efficiency of the PML. For both test cases, a non-harmonic wave is injected within the domain of interest and it is characterised by a Ricker wave. The first test case is the simplest one and will be used to confirm the ability of the PML to attenuate incident wave. It is composed of a bar separated in two parts: an elastic medium and a PML. We will shortly see that the scheme is efficient to attenuate incident waves with less than $1$ percent of the incident wave reflected. The second test case is a well known study case for seismic wave: the Lamb's test. It involves $3$ types of wave: pressure, shear and Rayleigh waves. This latter wave is a powerful surface wave, but it will be attenuated by the PML in a very efficient manner. Once again the efficiency of the PML will be estimated to less than $1 \%$ of incident wave reflected by the truncation interface. To be able to use the PML and to fit a specific simulation some advices will be given in this part. \\
Using the open source library Akantu, the reader is strongly advised to download the code and run the example presented in this report. In fact, they will constitute to the reader a good way to get hands-on training with Akantu and the PML method at the same time.        
%% Results


%% Conclusions




\end{abstract}


\newpage

\thispagestyle{empty}
\renewcommand{\abstractname}{Résumé}
\begin{abstract}
La méthode des bords absorbants est un concept utilisé en simulation numérique pour modéliser la propagation d'ondes en milieu infini. Plusieurs formulations et techniques existent pour construire ces bords. Par exemple, l'introduction d'une atténuation de type Rayleigh ou, comme présenté dans ce rapport, la méthode des couches parfaitement adaptées (PML: Perfectly matched layers). Ces techniques trouvent leur application dans de nombreux domaines comme l'éléctromagnétisme ou l'élastodynamique. A cause de la complexité de la formulation de ces PML, leurs construction et utilisation restent difficiles en pratique. Plusieurs formulations et implémentations ont été proposées pour résoudre certains problèmes comme l'instabilité ou même pour améliorer les performances.
Le but de ce rapport est de présenter la formulation stable de couches parfaitement adaptées à des problèmes en élastodynamique et à deux dimensions. \\
Dans un premier temps, la description complète et détaillée des équations régissant les PML sera faite. Nous partirons des équations du mouvement simple et par l'introduction de fonctions d'étirement, nous serons en mesure de formuler la forme forte des PML. S'inscrivant dans le contexte des éléments finis, la forme faible de ces équations sera décrite et partant de là nous présenterons sa formulation discrète en temps et en espace. L'implémentation de ce schéma numérique sera effectuée dans le logiciel Akantu qui est une librairie open source pour le calcul numérique dans la méthode des éléments finis. Cette librairie est développée au sein du Laboratoire de Simulation en Mécanique des Solides de l'Ecole Polytechnique Fédérale de Lausanne. Bien que ce schéma existe dans la littérature, il n'a jamais été implémenté et mis à disposition de manière open source. De plus, de nombreuses analyses de stabilité de schémas associés à des PML ont été effectuées mais cette formulation, bien qu'elle présente de nombreux avantages, n'a jamais été prouvée stable. Dans un second temps, nous étudierons donc la stabilité du schéma numérique précédemment décrit. Les schémas implicite et explicite seront analysés et seront prouvés respectivement inconditionnellement et conditionnellement stables. Certaines propriétés de ce schéma seront mis en exergue lors de cette analyse de stabilité comme par exemple la faculté que le schéma explicite possède à repousser la limite de stabilité imposée par le pas de temps critique. La dernière partie de ce rapport sera consacrée à la présentation et l'analyse de résultats numériques. Deux cas tests seront décrits: le premier est une simplification du problème à un cas uni-dimensionnel et le second est le cas test de Lamb. Une attention particulière sera portée à la réflexion de l'onde due à l'interface entre le milieu élastique et la PML. L'onde imposée en entrée est une onde de Ricker qui est une onde non-harmonique. Le premier cas test est constitué d'une barre et permet de montrer la capacité d'atténuation des ondes des PML. Nous serons en mesure de montrer que la PML permet d'atténuer plus de $99\%$ de l'onde incidente. La réflexion de l'onde due à l'interface entre les deux sous-domaines peut être minimisée par certains choix effectués au niveau des paramètres de la PML. Le test de Lamb permet de soumettre la PML à test bien connu des sismologues: la propagation d'une onde sismique dans un domaine supposé infini. Sans PML, l'analyse de l'onde est perturbée par sa réflexion aux bords du domaine. Une nouvelle fois la PML ne permettra la réflexion que de moins d'$1\%$ de l'onde incidente. Le futur utilisateur de la PML recevra dans cette dernière partie quelques conseils sur le choix des paramètres de la PML afin de minimiser cette réflexion indésirable et pour maximiser les performances du schéma numérique.      

\end{abstract}
\thispagestyle{empty}%


\newpage

\thispagestyle{empty}
\renewcommand{\abstractname}{Acknowledgments}
\begin{abstract}
First and foremost, I want to express my gratitude to Jean-François Molinari, director of the Computational Solid Mechanics Laboratory (LSMS) to have believed in my capacities and to have followed all stages of my works. For his expertise in the field of perfectly matched layers and coupling methods, I want to thank warmly Michael Brun, invited professor at LSMS. His numerous advices and feedbacks have greatly enriched this work. The analysis of the results of stability mainly due to the guidance of M. Brun. For their help concerning Akantu and the implementation of this project, I want to thank Guillaume Anciaux and Nicolas Richart, respectively research associate at LSMS and HPC application expert at Scitas. Their recommendations guided me during the process of coding the PML method within Akantu in an efficient manner, taking advantage of the different features the library. 
 
\end{abstract}
\thispagestyle{empty}%

\newpage

\tableofcontents

\newpage
\input{tex/nomenclature.tex}

\newpage

\input{tex/introduction}
\newpage
\input{tex/description.tex}
\newpage
\input{tex/stability.tex}
\newpage
\input{tex/results.tex}

\newpage
\input{tex/conclusion}


\newpage
%biblio
% Bibliographie
\bibliographystyle{plain}
\bibliography{biblio}
\end{document}
